Semi-Supervised Factored Logistic Regression for High-Dimensional Neuroimaging Data

### 2015-06-05 paper_nips/paper.tex
remove 1 *
typo
remove dropout

per-iteration tolerance of 1 * 10\textsuperscript{-8},

@@

higher bias and smaller variance then SSFLogReg with 100 latent directions.

@@

\paragraph{Miscellaneous observations.}
For the sake of completeness,
we informally report modifications of the statistical model
that did not improve generalization performance.
%
Introducing stochasticity into model learning by 
$a)$ input corruption of $\mathbf{X_{task}}$ or
$b)$ drop-out at the bottleneck $\mathbf{W_0}$ using binomial
distributions ($p=0.1, 0.3, 0.5$) deteriorated model performance
in all scenarios.
%
Adding $c)$ rectified linear units (ReLU) to $\mathbf{W_0}$ or
other commonly used nonlinearities ($d)$ sigmoid, $e)$ softplus,
$f)$ hyperbolic tangent) all led to decreased classification accuracies,
probably due to sample size limits.
%
Further, $g)$ ``pretraining'' of the bottleneck $\mathbf{W_0}$
(i.e., non-random initialization) by 
either corresponding SPCA or ICA loadings did not exhibit improved accuracies,
neither did $h)$ autoencoder pretraining.
%
Moreover,
introducing an additional $i)$ overcomplete layer (100 units)
after the bottleneck was not advantageous.
%
Finally, imposing either $j)$ only $\ell_1$ or 
$k)$ only $\ell_2$ penalty terms
was disadvantageous in all tested cases,
which favored ElasticNet regularization chosen in the above analyses.

>>>>

per-iteration tolerance of 10\textsuperscript{-8},

@@

higher bias and smaller variance than SSFLogReg with 100 latent directions.

@@

\paragraph{Miscellaneous observations.}
For the sake of completeness,
we informally report modifications of the statistical model
that did not improve generalization performance.
%
$a)$
Introducing stochasticity into model learning by 
%$a)$ 
input corruption of $\mathbf{X_{task}}$ %or
%% $b)$ drop-out at the bottleneck $\mathbf{W_0}$ using binomial
%% distributions ($p=0.1, 0.3, 0.5$) 
deteriorated model performance
in all scenarios.
%
Adding $b)$ rectified linear units (ReLU) to $\mathbf{W_0}$ or
other commonly used nonlinearities ($c)$ sigmoid, $d)$ softplus,
$e)$ hyperbolic tangent) all led to decreased classification accuracies,
probably due to sample size limits.
%
Further, $f)$ ``pretraining'' of the bottleneck $\mathbf{W_0}$
(i.e., non-random initialization) by 
either corresponding SPCA or ICA loadings did not exhibit improved accuracies,
neither did $g)$ autoencoder pretraining.
%
Moreover,
introducing an additional $h)$ overcomplete layer (100 units)
after the bottleneck was not advantageous.
%
Finally, imposing either $i)$ only $\ell_1$ or 
$k)$ only $\ell_2$ penalty terms
was disadvantageous in all tested cases,
which favored ElasticNet regularization chosen in the above analyses.
